%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Software Development Engineer} % Job title
    {Fiserv} % Organization
    {Chicago, IL} % Location
    {Mar. 2021 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Implemented payment methods and features for CommerceHub, Fiserv’s global omnichannel payments platform, utilizing the Java/Spring stack.}
            \item {Developed a settlement service for CommerceHub, enabling merchants to settle funds from their customers' payments, capable of processing millions of transactions per day.}
        \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {Software Development Engineer} % Job title
    {} % Organization
    {} % Location
    {Jul. 2019 - Mar. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and developed Apple Pay on the Web as a payment method for IPG Connect, Fiserv's hosted payment page, utilizing JavaScript/HTML for the front-end and Java/Spring for the back-end.}
            \item {Developed software to integrate TeleCheck (a check acceptance service) as a payment method into Fiserv's payment gateway.}
        \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Software Development Engineer} % Job title
    {First Data (acquired by Fiserv)} % Organization
    {Chicago, IL} % Location
    {Mar. 2018 - Jul. 2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed features and capabilities for digital wallet payment transactions made with Apple Pay, Google Pay, and Samsung Pay through First Data's payment gateway, utilizing both REST API and SOAP API.}
            \item {Developed software responsible for transmitting payment data from the payment gateway to front-end processors, card networks, and banks. This involved adhering to the ISO8583 protocol to appropriately prepare and package data elements for processor transmission.}
        \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Software Engineer} % Job title
    {Bluepay (merged with Clover)} % Organization
    {Chicago, IL} % Location
    {Apr. 2015 - Mar. 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed and maintained software for Bluepay's KPI and reporting system, which produced data analytics for over 140,000 merchants monthly and delivered 2,000+ reports each month, using SQL and Ruby.}
            \item {Built Ruby-based ETL solutions for KPIs extracting data from 30+ data sources.}
            \item {Converted the legacy KPI Reporting database from MS SQL Server to PostgreSQL, refactoring over 20,500 lines of SQL code.}
            \item {Created a Ruby on Rails application from scratch, providing report generation and configuration support for partners and sales teams. This application was utilized by operations and finance teams to manage payments of residuals and commissions.}
        \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Product Manager} % Job title
    {Hydro Flow Products, Inc} % Organization
    {Lake Zurich, IL} % Location
    {Apr. 2010 - Jul. 2014} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Led the product development of Fire Pump Tester Software, a SaaS solution designed for collecting, storing, and analyzing flow test data.}
            \item {Managed the redesign of the company's e-commerce website, resulting in a 25\% increase in the average number of unique visitors per month and a 9\% revenue growth over the following year.}
        \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
